### 2012-12-19 inst/examples/ricker-oscillate-example.Rmd
oscillatory example

```{r set-options, echo = FALSE, cache = FALSE, external = TRUE}
opts_chunk$set(external = TRUE, cache = FALSE, cache.path = "myers-cache/")
read_chunk('gaussian-process-control.R')
library(knitcitations)
```

@@

```{r Myer}
```

We use the model of `r citet("10.1126/science.269.5227.1106")`.

@@

With parameters `r p`.

```{r x0-obs}
x_0_observed <- K
```

@@

>>>>

```{r set-options, echo = FALSE, cache = FALSE, external = TRUE, include = FALSE}
opts_chunk$set(external = TRUE, cache = FALSE, cache.path = "myers-cache/")
read_chunk('gaussian-process-control.R')
library(knitcitations)
```

@@

```{r Ricker}
```

We use the Ricker model

@@

with parameters `r p`.

```{r x0-obs}
x_0_observed <- K
xT <- 0
set.seed(1111)
```

@@

```{r stationary_policy_only}
```
